Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-20 docs/questioning.tex
started with the metadata

	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} injection \\

@@

\begin{table*}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.99}{
    \begin{tabular}{l|c|ccc}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{3}{|c|}{Availability} \\
	&& \bf{Source Code}
	& \bf{Executable}
	& \bf{Testbed} \\
    \hline
	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & - & - & - \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & - & - & - \\ 
	&  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it Xu et al.}~\cite{XBS06}  & - & - & - \\
    &  	{\it {\sc wasc}}~\cite{NLC07} & - & - & - \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & - & - & - \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & - & - & - \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & - & - & - \\
	& 	{\it Stock et al.}~\cite{SLMS14} & - & - & - \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&   {\it {\sc sql}rand}~\cite{BK04} & - & - & - \\
	&   {\it Noncespaces}~\cite{GC09} & - & - & - \\ 
    &   {\it x{\sc js}}~\cite{APKLM10} & - & - & - \\
	\hline
	\hline    
	\multirow{13}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & - & - & - \\ 
	&   {\it BrowserShield}~\cite{RDWDE07} & - & - & - \\
	&   {\it CoreScript}~\cite{YCIS07} & - & - & - \\
	&   {\it {\sc met}}~\cite{ELX07} & - & - & - \\ 
    &   {\it {\sc beep}}~\cite{TNH07} & - & - & - \\
    &   {\it {\sc soma}}~\cite{OWVS08} & - & - & - \\
	&   {\it Blueprint}~\cite{LV09} & - & - & - \\
	&   {\it Phung et al.}~\cite{PSC09} & - & - & - \\
	&   {\it WebJail}~\cite{VDDPJ11} & - & - & - \\
	&   {\it ConScript}~\cite{ML10} & - & - & - \\
	&   {\it j{\sc csrf}}~\cite{PS11} & - & - & - \\
    &   {\it TreeHouse}~\cite{IW12} & - & - & - \\
   	&   {\it {\sc js}and}~\cite{AVBPDP12} & - & - & - \\
	\hline
	\hline  
        \multirow{12}{*}{Training}
    &   {\it {\sc didafit}}~\cite{LLW02} & - & - & - \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & - & - & - \\ 
	&   {\it Valeur et al.}~\cite{VMV05} & - & - & - \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & - & - & - \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & - & - & - \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & - & - & - \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & - & - & - \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & - & - & - \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & - & - & - \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & - & - & - \\
	& 	{\it Diglossia}~\cite{SMS13} & - & - & - \\
	\hline
    \end{tabular}}
    \caption{Availability of the corresponding mechanisms.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}

>>>>

	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc na},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection \\

@@

\begin{table*}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.99}{
    \begin{tabular}{l|c|ccc}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{3}{|c|}{Availability} \\
	&& \bf{Source Code}
	& \bf{Executable}
	& \bf{Testbed} \\
    \hline
	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & \xmark & \xmark & \xmark \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & - & - & - \\ 
	&  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it Xu et al.}~\cite{XBS06}  & - & - & - \\
    &  	{\it {\sc wasc}}~\cite{NLC07} & - & - & - \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & - & - & - \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & - & - & - \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & - & - & - \\
	& 	{\it Stock et al.}~\cite{SLMS14} & - & - & - \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&   {\it {\sc sql}rand}~\cite{BK04} & - & - & - \\
	&   {\it Noncespaces}~\cite{GC09} & - & - & - \\ 
    &   {\it x{\sc js}}~\cite{APKLM10} & - & - & - \\
	\hline
	\hline    
	\multirow{13}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & - & - & - \\ 
	&   {\it BrowserShield}~\cite{RDWDE07} & - & - & - \\
	&   {\it CoreScript}~\cite{YCIS07} & - & - & - \\
	&   {\it {\sc met}}~\cite{ELX07} & - & - & - \\ 
    &   {\it {\sc beep}}~\cite{TNH07} & - & - & - \\
    &   {\it {\sc soma}}~\cite{OWVS08} & - & - & - \\
	&   {\it Blueprint}~\cite{LV09} & - & - & - \\
	&   {\it Phung et al.}~\cite{PSC09} & - & - & - \\
	&   {\it WebJail}~\cite{VDDPJ11} & - & - & - \\
	&   {\it ConScript}~\cite{ML10} & - & - & - \\
	&   {\it j{\sc csrf}}~\cite{PS11} & - & - & - \\
    &   {\it TreeHouse}~\cite{IW12} & - & - & - \\
   	&   {\it {\sc js}and}~\cite{AVBPDP12} & - & - & - \\
	\hline
	\hline  
        \multirow{12}{*}{Training}
    &   {\it {\sc didafit}}~\cite{LLW02} & - & - & - \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & - & - & - \\ 
	&   {\it Valeur et al.}~\cite{VMV05} & - & - & - \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & - & - & - \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & - & - & - \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & - & - & - \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & - & - & - \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & - & - & - \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & - & - & - \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & - & - & - \\
	& 	{\it Diglossia}~\cite{SMS13} & - & - & - \\
	\hline
    \end{tabular}}
    \caption{Availability of the corresponding mechanisms.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}
